---
title: "Introduction to R"
output: 
  learnr::tutorial:
    css: css/styles.scss
    progressive: true
    allow_skip: true
runtime: shiny_prerendered
description: |
  Provides a basic introduction to R Programming.
---

```{r setup, include=FALSE}
library(learnr)
library(ggplot2)
library(gradethis)
library(ggcheck)
tutorial_options(exercise.timelimit = 30, 
                 exercise.checker = gradethis::grade_learnr,
                 exercise.pipe = NULL,
                 exercise.completion = FALSE)

gradethis_setup(exercise.reveal_solution = TRUE)
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction to R {data-progressive="FALSE"}

R is a popular multi-paradigm programming language to conduct statistical analysis. The motto of R is "Created by statisticians, for statisticians". Additionally, the programming language can be extended to implement new statistical techniques, create websites and dashboards (interactive software). Lastly, and most importantly, R can be downloaded and used for free.

### Learning Outcomes

::: contents
1.  Learn how to compute basic arithmetic using operators and functions.

2.  Learn the basics of using R functions to conduct tasks.

3.  Learn how R stores data into objects and how to classify data.

4.  Learn how to expand R's functionality by the use of packages.

5.  Learn how to conduct basic statistics and data visualizations.
:::

### 

```{r writing-1, echo=FALSE}
quiz(caption = "",
  question_text(
    "Name",
    answer(NULL, correct = TRUE),
    trim = TRUE,
    rows = 1,
    correct = NULL,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    allow_retry = TRUE),
  question_text(
    "Last 4 Digits of Student ID",
    answer(NULL, correct = TRUE),
    trim = TRUE,
    rows = 1,
    correct = NULL,
    try_again_button = "Edit Answer",
    incorrect = NULL,
    allow_retry = TRUE),
  question_text(
    "Make a prediction on what you think R can and cannot do.",
    answer(NULL, correct = TRUE),
    trim = TRUE,
    rows = 4,
    correct = NULL,
    try_again_button = "Edit Answer",
    incorrect = NULL,
  allow_retry = TRUE)
)
```

### Assignment

This tutorial has several code questions. In order to receive credit for a question, you must click the "Submit Answer" button on the R Code console. Click the "Next Topic" button to continue.

## Calculator

R can be thought as an advanced calculator. Type the following code in the code box and see what R prints out. Does the output correspond to what you expect to see?

Try `9+9`

```{r code-1, exercise = TRUE}

```

```{r code-1-check}
grade_result(
  pass_if(~ (.result == 9 + 9))
)
```

Try `9*9`

```{r code-2, exercise = TRUE}

```

```{r code-2-check}
grade_result(
  pass_if(~ (.result == 9 * 9))
)
```

Try `9-9`

```{r code-3, exercise = TRUE}

```

```{r code-3-check}
grade_result(
  pass_if(~ (.result == 9 - 9))
)
```

Try `9/9`

```{r code-4, exercise = TRUE}

```

```{r code-4-check}
grade_result(
  pass_if(~ (.result == 9 / 9))
)
```

Try `9+9+9`

```{r code-5, exercise = TRUE}

```

```{r code-5-check}
grade_result(
  pass_if(~ (.result == 9 + 9 + 9))
)
```

Try `9+9*9`

```{r code-6, exercise = TRUE}

```

```{r code-6-check}
grade_result(
  pass_if(~ (.result == 9 + 9 * 9))
)
```

Try `9+9/1`

```{r code-7, exercise = TRUE}

```

```{r code-7-check}
grade_result(
  pass_if(~ (.result == 9 + 9 / 1))
)
```

Try `9+(9+9)/9`

```{r code-8, exercise = TRUE}

```

```{r code-8-check}
grade_result(
  pass_if(~ (.result == 9 + (9 + 9) / 9))
)
```

Try `log(9, base=3)`

```{r code-9, exercise = TRUE}

```

```{r code-9-check}
grade_result(
  pass_if(~ (.result == log(9, 3)))
)
```

Try `exp(5)` (e\^5)

```{r code-10, exercise = TRUE}

```

```{r code-10-check}
grade_result(
  pass_if(~ (.result == exp(5)))
)
```

Try `3**3`

```{r code-11, exercise = TRUE}

```

```{r code-11-check}
grade_result(
  pass_if(~ (.result == 3**3))
)
```

Try `pi`

```{r code-12, exercise = TRUE}

```

```{r code-12-check}
grade_result(
  pass_if(~ (.result == pi))
)
```

Try `sin(pi*2)`

```{r code-13, exercise = TRUE}

```

```{r code-13-check}
grade_result(
  pass_if(~ (.result == sin(pi * 2)))
)
```

Try `sinpi(2)`

```{r code-14, exercise = TRUE}

```

```{r code-14-check}
grade_result(
  pass_if(~ (.result == sinpi(2)))
)
```

Try `tanpi(2)`

```{r code-15, exercise = TRUE}

```

```{r code-15-check}
grade_result(
  pass_if(~ (.result == tanpi(2)))
)
```

## Operators

Operators are symbols that tells R to conduct an operation. In the previous section, you were tasked to compute the values of certain formulas. To conduct these tasks, you used special symbols (known as operators) that tells R what to do with the numbers.

There are several operators that you can use in R classified as arithmetic, comparison, and special operators. Click "Continue" to learn more about them.

### 

### Arithmetic Operators

Arithmetic operators are symbols that tells R to conduct basic arithmetic such as add two numbers together. The table below provides some commonly used operators in R for arithmetic operations:

| Operator | Description        |
|----------|--------------------|
| \+       | Addition           |
| \-       | Subtraction        |
| \*       | Multiplication     |
| /        | Division           |
| \^       | Exponentiation     |
| %%       | Modulo (remainder) |
| %/%      | Integer division   |

### Comparison Operators

Comparison operators will compare to numbers (or data values) and return a logical value (`TRUE` or `FALSE`) indicating if the operation is valid or not. The table below provides some commonly used operators in R for comparison operations:

| Operator | Description              |
|----------|--------------------------|
| ==       | Equal to                 |
| !=       | Not equal to             |
| \>       | Greater than             |
| \<       | Less than                |
| \>=      | Greater than or equal to |
| \<=      | Less than or equal to    |
| !        | Negation                 |
| &        | Logical AND              |
| \|       | Logical OR               |

Try `5 <= 2`

```{r code-16, exercise = TRUE}

```

```{r code-16-check}
grade_result(
  pass_if(~ (.result == (5 <= 2)))
)
```

Try `cospi(2) == cos(2* pi)`

```{r code-17, exercise = TRUE}

```

```{r code-17-check}
grade_result(
  pass_if(~ (.result == (cospi(2) == cos(2* pi))))
)
```

Try `76 > 56`

```{r code-18, exercise = TRUE}

```

```{r code-18-check}
grade_result(
  pass_if(~ (.result == TRUE))
)
```

Try `76 < 56`

```{r code-19, exercise = TRUE}

```

```{r code-19-check}
grade_result(
  pass_if(~ (.result == FALSE))
)
```

Try `76 > 56 | 76 < 56`

```{r code-20, exercise = TRUE}

```

```{r code-20-check}
grade_result(
  pass_if(~ (.result == (76 > 56 | 76 < 56)))
)
```

Try `76 > 56 & 76 < 56`

```{r code-21, exercise = TRUE}

```

```{r code-21-check}
grade_result(
  pass_if(~ (.result == (76 > 56 & 76 < 56)))
)
```

```{r writing-2, echo=FALSE}
question_text(
  "Looking at the previous two examples, why do you think you get different results when you switch from '|' to '&'?",
  answer(NULL, correct = TRUE),
  trim = TRUE,
  rows = 4,
  correct = NULL,
  try_again_button = "Edit Answer",
  incorrect = NULL,
  allow_retry = TRUE)

```

### Special Operators

The table below provides some commonly used operators in R for special operations:

| Operator | Description              |
|----------|--------------------------|
| %in%     | Element-wise membership  |
| \<-      | Assignment               |
| -\>      | Right-to-left assignment |
| %\*%     | Matrix multiplication    |
| %o%      | Outer product            |
| %x%      | Kronecker product        |
| \|\>     | Pipe operator            |
| %\>%     | Pipe operator            |

## Functions

An R function is a procedure that tells R to do certain tasks. For example, `log(x)` is an R function that takes the value `x` and provides you the natural logarithm. Here `x` is known as an argument which needs to be specified to us the `log()` function. Find the `log(x = 5)`

```{r code-22, exercise = TRUE}

```

```{r code-22-check}
grade_result(
  pass_if(~ (.result == log(5)))
)
```

Another argument for the `log()` function is the `base` argument. In the previous code, we did not specify a value for the `base` argument, so R used the default value for the `base` argument, the number **e**. If you want to use the common log with base 10, you will need to set the `base` argument equal to 10.

Try `log(x = 5, base = 10)`

```{r code-23, exercise = TRUE}

```

```{r code-23-check}
grade_result(
  pass_if(~ (.result == log(5, 10)))
)
```

Now try `log(5, 10)`

```{r code-24, exercise = TRUE}

```

```{r code-24-check}
grade_result(
  pass_if(~ (.result == log(5, 10)))
)
```

Notice that it provides the same value. When no arguments are specified, R will assign values to the arguments based on the inputs (value) position in the function.  For `log(5, 10)`, R thinks that 5 corresponds to the first argument `x` and 10 is the second argument `base`.

## Data Types

In R, there are several data types you can use to conduct complex analysis. These data types tells R how to conduct an analysis. For example, when you give R a number, it will evaluate what type it is and conduct a specific task, such as an arithmetic operation. Click "Continue" to see the most commonly used data types.

### 

| Data Type | Description                                         |
|-----------|-----------------------------------------------------|
| Numeric   | Represents numeric values (real or decimal numbers) |
| Integer   | Represents whole numbers without decimal points     |
| Logical   | Represents boolean values (TRUE or FALSE)           |
| Character | Represents text or string values                    |
| POSIXct   | Represents date and time values                     |
| NULL      | Represents absence of a value                       |

### 

In R, you can test whether a value is a certain data by using the general `is.X()` function where you replace `X` with a data type you suspect.

Try `is.numeric(pi)`

```{r code-25, exercise = TRUE}

```

```{r code-25-check}
grade_result(
  pass_if(~ (.result == is.numeric(pi)))
)
```

Try `is.numeric(TRUE)`

```{r code-26, exercise = TRUE}

```

```{r code-26-check}
grade_result(
  pass_if(~ (.result == is.numeric(TRUE)))
)
```

Try `is.integer(2)`

```{r code-27, exercise = TRUE}

```

```{r code-27-check}
grade_result(
  pass_if(~ (.result == is.integer(2)))
)
```

Try `is.integer(2L)`

```{r code-28, exercise = TRUE}

```

```{r code-28-check}
grade_result(
  pass_if(~ (.result == is.integer(2L)))
)
```

```{r writing-3, echo=FALSE}
question_text(
  "Looking at the previous two examples, why do you think you get different results when you use 'L'?",
  answer(NULL, correct = TRUE),
  trim = TRUE,
  rows = 4,
  correct = NULL,
  try_again_button = "Edit Answer",
  incorrect = NULL,
  allow_retry = TRUE)

```

## Objects

One major component in R are R objects. R objects can be thought as virtual containers of things. These objects can store results, numbers, functions, and much more. Here we will work on a few concepts with R objects. First, let's learn how to create an R object. To create an R object called `x` that contains the number 12, use the `<-` operator. The `<-` operator is just the less than arrow `<` and minus sign `-`. Type `x <- 12`.

```{r code-29, exercise = TRUE}

```

```{r code-29-solution}
x <- 12
```

```{r code-29-check}
grade_result(
  pass_if(~ identical(.result, x <- 12))
)
```

Notice that nothing prints out. This is because R does not need to print out any results. Now to view what is in `x`, just type `x`.

```{r code-30-setup}
x <- 12
```

```{r code-30, exercise = TRUE, exercise.setup = "code-30-setup"}

```

```{r code-30-solution}
# Arrow ----
x

# Non Arrow ----
print(x)
```

```{r code-30-check}
grade_this_code()
```

Notice that the number 12 pops out.

Now try to add something to the R object `x`. Type `x + 3`

```{r code-31, exercise = TRUE, exercise.setup = "code-30-setup"}

```

```{r code-31-solution}
 x + 3
```

```{r code-31-check}
grade_this_code()
```

Notice that 15 prints out.

Now try other calculations to `x`

```{r code-32, exercise = TRUE, exercise.setup = "code-30-setup"}

```

### Vectors

Vector can be thought as a set of data points. Each data point is known as an element in a vector. The length of a vector is the number of elements contained. Additionally, all element have the same data type.

The best way to create a vector is by using the `c()` function. This combines values together to create a vector. Create a vector called `my_vec` and put the numbers one to ten:

```{r code-33-setup}
my_vec <- c(1,2,3,4,5,6,7,8,9,10)
```

```{r code-33, exercise = TRUE}

```

```{r code-33-solution}
# c approach -----
my_vec <- c(1,2,3,4,5,6,7,8,9,10)

# colon -----
my_vec <- 1:10
```

```{r code-33-check}
grade_this_code()
```

::: {#code-33-hint}
Try typing each number inside the `c()` and separate them by commas.
:::

To view what is inside the vector, type the name of vector (`my_vec`):

```{r code-34, exercise = TRUE, exercise.setup = "code-33-setup"}

```

```{r code-34-solution}
my_vec
```

```{r code-34-check}
grade_this_code()
```

To find the length of the vector, use the `length()` function:

```{r code-35, exercise = TRUE, exercise.setup = "code-33-setup"}

```

```{r code-35-solution}
length(my_vec)
```

```{r code-35-check}
grade_this_code()
```

::: {#code-35-hint}
Type the name of the object inside the `length()`.
:::

### Data Frames

Data Frames is an R object that can be thought of as R's version of a data set.

### 

::: info
#### What is a data set?

A data set is a method to store information about an experimental unit. The rows shows the characteristics (data) related each specific experimental unit, and the columns explains what the data characteristic.
:::

### 

#### Structure of a data frame

The structure of a data frame is similar to a data set, the rows represent a single observation, and the columns represent the variables. For example type `head(mtcars)` to view the first six observations of the `mtcars` data frame,

```{r code-36, exercise=TRUE}

```

```{r code-36-solution}
head(mtcars)
```

```{r code-36-check}
grade_this_code()
```

Here each row represents a car and each column represents measurements of the car.

For this class, we will want to access variable in data frames. The general code to access a variable is to specify the name of the data frame, typing the `$` symbol, and then the name of the variable. In other words, to code follows this form: `DATA$VARIABLE`. This tells R to look in the `DATA` data frame and get the `VARIABLE` variable. Now using the `mtcars` data set, print out the `mpg` variable:

```{r code-37, exercise=TRUE}

```

```{r code-37-solution}
mtcars$mpg
```

```{r code-37-check}
grade_this_code()
```

Notice that R prints out a set of numbers. This looks very similar to a vector that we worked out before. Use the `is.vector()` function to determine if the variable `mtcars$mpg` is a vector:

```{r code-38, exercise=TRUE}

```

```{r code-38-solution}
mtcars$mpg |> is.vector()
```

```{r code-38-check}
grade_this_code()
```

### 

If you want to know what variables are in a data frame, use the `names()`. What are the variables of `mtcars`?

```{r code-39, exercise=TRUE}

```

```{r code-39-solution}
names(mtcars)
```

```{r code-39-check}
grade_this_code()
```

::: {#code-39-hint}
`mtcars` can be used as the input for the function.
:::

## Packages

R can be extended to do more things, such as create this tutorial. This is done by installing R packages. An R package can be thought of as extra software. This allows you to do more with R. To install an R package, you will need to use `install.packages("NAME_OF_PACKAGE")`. Once you install it, you do not need to install it again. To use an R package, use `library("NAME_OF_PACKAGE")`. This allows you to load the package in R. You will need to load the package every time you start R. For more information, please watch the video below.

```{=html}
<iframe src="https://player.vimeo.com/video/203516241?h=819422ce1e&color=428bca" width="640" height="400" frameborder="0" allow="autoplay; fullscreen; picture-in-picture" allowfullscreen></iframe>
<p><a href="https://vimeo.com/203516241">install Packages</a> from <a href="https://vimeo.com/rstudioinc">RStudio, Inc.</a> on <a href="https://vimeo.com">Vimeo</a>.</p>
```
## Data Summarizations

Here, we will go over some of the basic syntax to obtain basic statistics. We will use the variables `mpg` and `cyl` from the `mtcars` data set. To view the data set use the `head()`:

```{r code-40, exercise = TRUE}

```

```{r code-40-solution}
head(mtcars)
```

The variable `mpg` would be used as a continuous variable, and the variable `cyl` would be used as a categorical variable.

### 

### Point Estimates

```{r writing-4, echo=FALSE}
question_text(
  "Describe in your words what is the definition of a point estimate.",
  answer(NULL, correct = TRUE),
  correct = NULL,
  rows = 4,
  try_again_button = "Edit Answer",
  incorrect = NULL,
  allow_retry = TRUE
)

```

### 

The first basic statistic you can compute are point estimates. These are your means, medians, etc. Here we will calculate these estimates.

#### Mean

To obtain the mean, use the `mean()`, you only need to specify `x=` for the data to compute the mean:

```{r code-41, exercise = TRUE}

```

```{r code-41-solution}
mean(mtcars$mpg)
```

```{r code-41-check}
grade_this_code()
```

#### Median

To obtain the median, use the `median()`, you only need to specify `x=` for the data to compute the median:

```{r code-42, exercise = TRUE}

```

```{r code-42-solution}
median(mtcars$mpg)
```

```{r code-42-check}
grade_this_code()
```

#### Frequency

To obtain a frequency table, use the `table()`, you only need to specify the data as the first argument to compute the frequency table:

```{r code-43, exercise = TRUE}

```

```{r code-43-solution}
table(mtcars$cyl)
```

```{r code-43-check}
grade_this_code()
```

#### Proportion

To obtain a the proportions for the frequency table, use the `prop.table()`. However the first argument must be the results from the `table()`. Use the `table()` inside the `prop.table()` to get the proportions:

```{r code-44, exercise = TRUE}

```

```{r code-44-solution}
prop.table(table(mtcars$cyl))
```

```{r code-44-check}
grade_this_code()
```

### Variability

```{r writing-5, echo=FALSE}
question_text(
  "Describe in your words what is the definition of variability.",
  answer(NULL, correct = TRUE),
  correct = NULL,
  rows = 4,
  try_again_button = "Edit Answer",
  incorrect = NULL,
  allow_retry = TRUE
)

```

### 

Variability statistics can describes the average deviation of data points from a central tendency (point estimate). It can be thought as how far the data points are from the center. R is capable of calculating several variability statistics.

#### Variance

To obtain the variance, use the `var()`, you only need to specify `x=` for the data to compute the variance:

```{r code-45, exercise = TRUE}

```

```{r code-45-solution}
var(mtcars$mpg)
```

```{r code-45-check}
grade_this_code()
```

#### Standard deviation

To obtain the standard deviation, use the `sd()`, you only need to specify `x=` for the data to compute the standard deviation:

```{r code-46, exercise = TRUE}

```

```{r code-46-solution}
sd(mtcars$mpg)
```

```{r code-46-check}
grade_this_code()
```

#### Max and Min

To obtain the max and min, use the `max()` and `min()`, respectively. You only need to specify the data as the first argument to compute the max and min:

```{r code-47, exercise = TRUE}

```

```{r code-47-solution}
max(mtcars$mpg)
min(mtcars$mpg)
```

```{r code-47-check}
grade_this_code()
```

#### Q1 and Q3

To obtain the Q1 and Q3, use the `quantile()` and specify the desired quantile with `probs=`. You only need to specify the data as the first argument and `probs=` (as a decimal) to compute the Q1 and Q3:

```{r code-48, exercise = TRUE}

```

```{r code-48-solution}
quantile(mtcars$mpg,.25)
quantile(mtcars$mpg,.75)
```

```{r code-48-check}
grade_this_code()
```

## Data Visualizations

R has several built-in functions to create extraordinary plots. Some of the most commonly used functions are `plot()` and `hist()`. However, several R developers have create several R packages that make it easier to create extraordinary plots. In this section, we will explore the `ggplot2` package, which provides several graphical functions, to create basic graphs. The plot below is an example of what can be achieved using `ggplot2`:

```{r ex-1, fig.alt="A Scatter Plot showing the relationship between weight and miles per gallon. Stratified by Engine and Transmission Type", echo=FALSE, message=FALSE}
ggplot(mtcars, aes(wt, mpg, color = factor(vs))) + 
  geom_point() +
  geom_smooth(method = "lm", se = F) +
  facet_wrap(~am, 
             labeller = labeller(am = c("0" = "Automatic", "1" = "Manual"))) +
  xlab("Weight (1000 lbs)") +
  ylab("Miles Per Gallon") +
  labs(color = "Engine Type",
       title = "Weight vs Miles Per Gallon",
       subtitle = "Stratified By Engine and Transmission Type") +
  scale_color_discrete(labels = c("V-Shaped", "Straight")) +
  theme_bw()
```

For more information on plotting with `ggplot2`, please visit their main [website](https://ggplot2.tidyverse.org/) or the ggplot2 [cookbook](https://r-graphics.org/).

To begin, the `ggplot2` package really works well when you are using data frames. If you have any output that is not a data frame that you want to plot (vector, matrix, list), convert into to a data frame. Once we have our data set, the first thing you would want to do is specify the main components of your base plot. This will be what will be plotted on your x- and y-axis. Next, you will add what type of plot you want to create. Lastly, you will add different layers to tweak the plot. This can be changing the layout or even overlaying another plot. The `ggplot2::` provides you with tools to do almost everything you need to create a plot easily.

Before we begin plotting, load the `ggplot2` package in R.

```{r code-49, exercise = TRUE}

```

```{r code-49-solution}
library(ggplot2)
```

### 

The main function to use is the `ggplot()` function, which will create a base plot using the `data` argument and the `mapping` argument. The `data` argument specifies which data frame you should used for the base plot and the `mapping` argument. The `mapping` argument will tell the `ggplot()` how to set up the x- and y-axis of a plot. This is achieved by using the `aes()` function, which constructs the mapping function for the base plot. The `aes()` requires the `x` and optionally the `y` arguments to set which values represents the x- and y- axis. The `aes()` also accepts other arguments for grouping or other aesthetics.

To begin, create a base plot using the `mtcars` data frame and map the `mpg` variable.

```{r code-50, exercise=TRUE}

```

```{r code-50-solution}
ggplot(mtcars, aes(mpg))
```

```{r code-50-check}
grade_this_code()
```

Now that the base plot has been created, we can tell `ggplot` how we want to visualize the data using the `geom_*()` family of functions. For example, we can create histogram by adding (`+`) `geom_histogram()` to the base plot:

```{r ex-2, echo=TRUE, fig.alt="An image showing a histogram of the miles per gallon in the mtcars data set.", message=FALSE}
ggplot(mtcars, aes(mpg)) + geom_histogram() 
```

Notice, how we use the `+` sign to modify the plot. Below is a limited list of different types of geoms we can add to the plot.

| `geom_*()`   | Description                         |
|--------------|-------------------------------------|
| `histogram`  | Constructs a Histogram              |
| `density`    | Constructs a Density Plot           |
| `dotplot`    | Constructs a Dot Plot               |
| `qq`         | Constructs a Quantile-Quantile Plot |
| `bar`        | Constructs a Bar Plot               |
| `boxplot`    | Constructs a Box Plot               |
| `point`      | Constructs a Scatter Plot           |
| `line`       | Constructs a Line Plot              |
| `jitter`     | Constructs a Jitter Plot            |
| `smooth`     | Add a Smooth Line to Plot           |
| `violin`     | Constructs a Violin Plot            |
| `density_2d` | Constructs a 2D Kernel Density Plot |
| `contour`    | Constructs a Contour Map            |

### Box Plot

Create a box plot using the base plot above.

```{r code-51, exercise=TRUE}

```

```{r code-51-solution}
ggplot(mtcars, aes(mpg)) + geom_boxplot()
```

```{r code-51-check}
grade_result(
  pass_if( ~uses_geoms(.result, "boxplot", exact = FALSE))
)
```

### Scatter Plot

Create a scatter plot using the `wt` and `mpg` variables from the `mtcars` data set. Note you will now need to change your base plot code to incorporate `wt`.

```{r code-52, exercise=TRUE}

```

```{r code-52-solution}
ggplot(mtcars, aes(wt, mpg)) + geom_point()
```

```{r code-52-check}
grade_this_code()
```

### Scatter Plot with Regression Line

Using the plot you created above, add a regression line to the code using `geom_smooth(method = "lm", se = F)` (the `method` argument tells ggplot to use a line, the `se = F` indicates not to use error bars).

```{r code-53, exercise=TRUE}

```

```{r code-53-solution}
ggplot(mtcars, aes(wt, mpg)) + 
  geom_point() +
  geom_smooth(method = "lm", se = F)
```

```{r code-53-check}
grade_this_code()
```

###

As you can see the plots can be enhanced with the addition of several arguments and functions. The code for the plot at the beginning of this sections can be found below:

```{r ex-3, fig.alt="A Scatter Plot showing the relationship between weight and miles per gallon. Stratified by Engine and Transmission Type", echo=TRUE, message=FALSE}
ggplot(mtcars, aes(wt, mpg, color = factor(vs))) + 
  geom_point() +
  geom_smooth(method = "lm", se = F) +
  facet_wrap(~am, 
             labeller = labeller(am = c("0" = "Automatic", "1" = "Manual"))) +
  xlab("Weight (1000 lbs)") +
  ylab("Miles Per Gallon") +
  labs(color = "Engine Type",
       title = "Weight vs Miles Per Gallon",
       subtitle = "Stratified By Engine and Transmission Type") +
  scale_color_discrete(labels = c("V-Shaped", "Straight")) +
  theme_bw()
```

## Quiz

### Questions

```{r quiz, echo=FALSE}
quiz(caption = "",
  question("Which function do you need to use to properly load an R package?",
    answer("install.packages()", message = "This will install an R package."),
    answer("load()", message = sprintf("This is used to load data, not a package.")),
    answer("library()", correct = TRUE),
    answer("require()", message = "While this will work, it is advised not to use this function."),
    allow_retry = TRUE,
    random_answer_order = TRUE
  ),
  question("What is the code to add 5 to 4 squared?",
    answer("5 + 4**2", correct = TRUE),
    answer("5 * 4 && 4", message = "This utilizes the modulo operator."),
    answer("4^2 + 5", correct = TRUE),
    answer("4*4 + 5", correct = TRUE),
    incorrect = "Incorrect. There is at least one more thing.",
    allow_retry = TRUE,
    random_answer_order = TRUE
  ),
    question("Which operator is used to create an R object with data? ",
    answer("<-", correct = TRUE),
    answer("==", message = "This is the absolute equal operator."),
    answer("=", correct = TRUE),
    answer("<<", message = "This is not a known operator"),
    allow_retry = TRUE,
    random_answer_order = TRUE
  ),
  question("Which one is the pipe operator?",
    answer("|>", correct = TRUE),
    answer("%|%", message = "This is not a known R operator."),
    answer("%>%", correct = TRUE),
    answer("%%", message = "This is the modulo (remainder) operator."),
    allow_retry = TRUE,
    random_answer_order = TRUE
  ),
  question("Do you need to specify the name of the argument for a function?",
           answer("TRUE"),
           answer("FALSE", correct = T),
           allow_retry = TRUE),
  question("Which function tells you if a data value is a Logical value?",
           answer("if.logical()"),
           answer("as.logical()"),
           answer("is.logical()", correct = TRUE),
           allow_retry = TRUE,
           random_answer_order = TRUE
           )
)
```

```{r writing-6, echo=FALSE}
  question_text(
  "Write a reflection on what you had learned about R Basics.",
  answer(NULL, correct = TRUE),
  trim = TRUE,
  rows = 4,
  try_again_button = "Edit Answer",
  correct = NULL,
  incorrect = NULL,
  allow_retry = TRUE)
```

### Coding Questions

#### Problem 1

Given the following equation:

$$
Y= X^2+\log(X) + \sin(2\pi X)
$$ Write the code that will find the value of $Y$ when $X=10$?

```{r qcode_1, exercise=TRUE}

```

```{r qcode_1-check}
grade_result(
  pass_if(~ (.result == 100+log10(10)+sinpi(10)))
)
```

#### Problem 2

Find mean river length in North America from the `rivers` vector.

```{r qcode_2, exercise=TRUE}

```

```{r qcode_2-check}
grade_result(
  pass_if(~ (.result == mean(rivers)))
)
```

#### Problem 3

Find the 95th percentile of river length in North America from the `rivers` vector.

```{r qcode_3, exercise=TRUE}

```

```{r qcode_3-check}
grade_result(
  pass_if(~ (.result == quantile(rivers, probs = .95)))
)
```

#### Problem 4

Using the `faithful` data set, create a scatter plot using the variables `eruptions` and `waiting`. Store the plot in the object `p`

```{r qcode_4, exercise=TRUE}

```

```{r qcode_4-check}
grade_result(
  pass_if(~ (uses_aesthetics(.result, c("eruptions", "waiting")) & uses_geom(.result, "point")))
)
```

## Submit Responses

```{r context="server"}
learnrhash::encoder_logic()
```

```{r encode, echo=FALSE}
learnrhash::encoder_ui(
  ui_before = shiny::div(
    "If you have completed this tutorial and are happy with all of your",
    "solutions, please click the button below to generate your hash and",
    "submit it using the corresponding tutorial assignment tab on your Learning Management System, if needed.",
    shiny::tags$br()
  ))
```
